\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%       06-08-2020
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%   Sandesh Singh Resume(First year end)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Sandesh Singh}{ \urlstyle{same}{ Sophomore }|{ Mechanical Engineering }| { IIT Jodhpur }\\
singh.81@iitj.ac.in | +91-9987557785 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.30\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIT JODHPUR}
\descript{B.Tech in Mechanical Engg.}
\descript{ Department Rank: 1 }
\descript{ Current CGPA: 8.51 / 10 }
\location{May 2023 | Jodhpur, India}
\sectionsep

\subsection{THAKUR VIDYA MANDIR}
\descript{Class 12 | HSC}
\descript{ Percentage: 88.2\%}
\location{May 2019 | Mumbai, India}
\sectionsep

\subsection{THAKUR Int'l. SCHOOL}
\descript{Class 10 | ICSE}
\descript{ Percentage: 96.8\%(agg.)}
\location{May 2017 | Mumbai, India}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
\location{Proficient:}
\textbullet{} Python \textbullet{}   C \textbullet{} C++\\
\textbullet{} Dart \textbullet{} HTML \textbullet{} CSS \\
\location{Familiar:}
\textbullet{} Java \textbullet{} Javascript \textbullet{} Solidity\\
\textbullet{} Matlab \textbullet{} GraphQL \textbullet{} Latex \\
\sectionsep

\subsection{Development}
\textbullet{} Django \textbullet{} Flutter \textbullet{}  Vue.js  \\
\textbullet{} Git \textbullet{} Firebase \textbullet{} Adobe XD \\
\sectionsep

\subsection{Other Skills}
\textbullet{} Competitive Programming \\
\textbullet{} Solidworks \textbullet{} AutoCAD \\
\textbullet{} Public Speaking \textbullet{} Debating  \\
\textbullet{} Webinar Host \textbullet{} Quizzing \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
GitHub:// \href{https://github.com/Sandesh1013}{\bf Sandesh1013 \faExternalLink}\\
LinkedIn://  \href{https://www.linkedin.com/in/sandesh-singh-1596281a0/}{\bf Sandesh Singh \faExternalLink} \\
CodeChef:// \href{https://www.codechef.com/users/sandesh77}{\bf sandesh77 \faExternalLink} \\
CodeForces:// \href{https://codeforces.com/profile/Sandesh1013}{\bf Sandesh1013 \faExternalLink} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Introduction To Computer Science \\
Linear Algebra \\
Calculus and Differential Equations\\
Introduction to Machine Learning\\
Data Structures and Algorithms\\
Scientific Computations \\
\subsection{MOOC'S}
Flutter and Dart-The Complete Guide \\
Responsive Web Design \\
Django Developer Bootcamp\\
Ethereum and Solidity*\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{StopStalk App}
\descript{| Flutter Developer }
\location{November 2020 - Present | \href{https://github.com/devlup-labs/stopstalk-android}{\bf GitHub \faExternalLink} }
\location{}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Collaborating with the popular Sport Programming website-StopStalk,to develop and publish a cross-platform mobile application. 
\item Implemented searching functionalities,dynamic problem recommendation by querying from a Firebase backend and JSON for realtime updates.
\item Developed many frontend components and screens to provide excellent UI/UX.
\item Tech-stack:\textbf{Flutter,Firebase,Web2py}
\end{tightemize}
% \sectionsep
\section{Projects}
\runsubsection{Sequential Feature Selection}
\descript{| Course Project }
\location{December 2020 - January 2021 | \href{https://github.com/Sandesh1013/IML-CSL2010-Project}{\bf GitHub \faExternalLink} }
\begin{tightemize}
\item Analysis and self-implementation of Bayesian Network Classifiers versus K-NN Classifier using Sequential Feature Selection.
\item Tech-stack:\textbf{Python,Scikit-Learn}
\end{tightemize}
% \sectionsep
\runsubsection{Lokalite}
\descript{| Junior Flutter Developer }
\location{May 2020 - July 2020 |
 \href{https://gitlab.com/lokalite/app}{\bf GitLab \faExternalLink} }
\begin{tightemize}
\item Helped develop a market-ready App to provide communication,information and more between shops and restaurants, directly to the consumer.
\item Created multiple UI components and worked/tested with a backend system.
\item Tech-stack:\textbf{Flutter,Django}
\end{tightemize}
% \sectionsep
\runsubsection{\href{https://github.com/devlup-labs/devlup-labs.github.io} DevlUp Labs Portfolio \faExternalLink}
\descript{| Developer }
\location{April 2020 - July 2020 | \href{https://github.com/devlup-labs/devlup-labs.github.io}{\bf GitHub \faExternalLink} }
\begin{tightemize}
\item Developed a dynamic progressive Web-App for DevlUps Labs,the Open Source Community at IITJ and oversaw future extensions on the project. 
\item Implemented automation by fetching information from various API's and dynamically rendering them with a Javascript Framework design. 
\item Tech-stack:\textbf{Vue.js,Vuetify,Javascript}
\end{tightemize}
% \sectionsep
\runsubsection{PowerBank Rental System}
\descript{| Engineering Design Project }
\location{September 2019 - July 2020 | \href{https://drive.google.com/drive/folders/16Lj2Nk9W2i14liwNPwqcfH4u3RYZyAHY?usp=sharing}{\bf Drive \faExternalLink} }
\begin{tightemize}
\item Led a team of 8 members to conceptualise and work on a complete rental system for power banks(similar to Yulu in concept).
\item Implemented a visual 3D render using Solidworks for the hardware components and draughted a mobile application for this system.
\item Tech-stack:\textbf{Solidworks,Flutter,Arduino}
\end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
\begin{tabular}{rll}
2020 &\href{https://iitj.ac.in/uploaded_docs/summer\%20challenge_revised_03112020.pdf}{\bf{Institute Summer Challenge \faExternalLink: }}2nd place on a research paper on WASH \\
2019 &\textbf{JEE-19:}Among top 0.6\% percentile of 1.3 million Applicants in JEE- 2019\\
2019 &\textbf{12th  HSC:}Top 1\% of Maharashtra HSC examination\\
\end{tabular}

\section{Positions of Responsibility}
\begin{tabular}{rll}
2021-Present	     & \textbf{Overall Head} of the \textbf{Entrepreneurship Cell, IIT Jodhpur} for the year 2021\\
2020-Present	     & \textbf{Student Guide} of the \textbf{Student Wellbeing Committee, IIT Jodhpur} \\
\end{tabular}

\section{Extracurricular}
\textbf{Core Member, DevlUp Labs} an open-source organisation of IIT Jodhpur.\\
Represented IIT J in the \textbf{Quizzing Team} and \textbf{Parliamentary Debate} at the Inter-IIT Cult. Meet.\\
\textbf{Quiz Club Moderator} for 2020-21,having won several college-level Quizzes.\\
\textbf{Hosted} several events including Ignus, IIT J's Cultural fest and Spandan the Intra-College fest. \\
A member of IIT Jodhpur's \textbf{Table-Tennis} team\\
\end{minipage}
\end{document}  \documentclass[]{article}
